Machine Learning Approaches for Ammonia Volatilization Prediction after Manure Application

### 2024-04-26 manuscript.qmd
removing relative emission of the Part 1

        select (pmid, time, e, er) %>%

        mutate (truth_e = data_alfam2$e.cum) %>%
        mutate (truth_er = data_alfam2$e.rel) %>%

@@

        select (pmid, time, e, er, truth_e, truth_er, dataset) %>%

@@

    mutate (e.rel_hat = e.cum_hat / tan.app) %>%

    select (pmid, time, e = e.cum_hat, er = e.rel_hat, truth_e = e.cum, truth_er = e.rel, dataset)    
```

@@

```{r}
df_evaluation_metrics = rbind (

    predictions_of_all_methods %>% 
        select (prediction = e, truth = truth_e, dataset, method) %>% 
        mutate (name = "72h cum. emission"),

    predictions_of_all_methods %>% 
        select (prediction = er, truth = truth_er, dataset, method) %>% 
        mutate (name = "72h relative cum. emission")

@@

        .by = c (name, dataset, method)

@@

    rename (response = name) %>%
    pivot_longer (cols = c (Pearsons_r, ME, MAE, MBE)) %>%
    mutate (name = factor (name, levels = c("Pearsons_r", "ME", "MAE", "MBE"))) %>% 
    filter (name %in% c ("MAE", "MBE")) %>%

@@

    mutate (variation = (1 - abs(value) / abs(value [method == "alfam2"])) * 100, .by = c(response, name, dataset))
```

```{r, fig.width = 16, fig.height = 5}
# Evaluation for 72h cum. emission
df_plot = df_evaluation_metrics %>%
    filter (name == "72h cum. emission" & dataset == "Evaluation subset") %>%
    select (- name) %>%
    pivot_longer (cols = c (Pearsons_r, ME, MAE, MBE)) %>%
    mutate (name = factor (name, levels = c("Pearsons_r", "ME", "MAE", "MBE")))

@@

```{r, fig.width = 16, fig.height = 5}
# Evaluation for 72h relative cum. emission
df_plot = df_evaluation_metrics %>%
    filter (name == "72h cum. emission" & dataset == "Calibration subset") %>%
    select (- name) %>%
    pivot_longer (cols = c (Pearsons_r, ME, MAE, MBE)) %>%
    mutate (name = factor (name, levels = c("Pearsons_r", "ME", "MAE", "MBE")))

>>>>

        select (pmid, time, e) %>%

        mutate (truth_e = data_alfam2$e.cum) %>%

@@

        select (pmid, time, e, truth_e, dataset) %>%

@@

    select (pmid, time, e = e.cum_hat, truth_e = e.cum, dataset)    
```

@@

```{r}
df_evaluation_metrics = predictions_of_all_methods %>%

    select (prediction = e, truth = truth_e, dataset, method) %>%

@@

        .by = c (dataset, method)

@@

    pivot_longer (cols = c (Pearsons_r, ME, MAE, MBE)) %>%
    mutate (name = factor (name, levels = c("Pearsons_r", "ME", "MAE", "MBE"))) %>% 
    filter (name %in% c ("MAE", "MBE")) %>%

@@

    mutate (variation = (1 - abs(value) / abs(value [method == "alfam2"])) * 100, .by = c(name, dataset))
```

```{r, fig.width = 16, fig.height = 5}
# Evaluation for 72h cum. emission
df_plot = df_evaluation_metrics %>%
    filter (dataset == "Evaluation subset") %>%
    pivot_longer (cols = c (Pearsons_r, ME, MAE, MBE)) %>%
    mutate (name = factor (name, levels = c("Pearsons_r", "ME", "MAE", "MBE")))

@@

```{r, fig.width = 16, fig.height = 5}
# Evaluation for 72h relative cum. emission
df_plot = df_evaluation_metrics %>%
    filter (dataset == "Calibration subset") %>%
    pivot_longer (cols = c (Pearsons_r, ME, MAE, MBE)) %>%
    mutate (name = factor (name, levels = c("Pearsons_r", "ME", "MAE", "MBE")))
